### 2020-01-16 ChapterResults/chapterResults.tex
Updated: Result graphs replotted and split into individual figures

\subsection{Control Experiment}
A control experiment on a centralised system (single server, single simulation) was performed, in which the scenario was repeated multiple times. The speed of each object is increased from $1$ to $64m\mathord{\cdot}s^{-1}$ in steps of $1m\mathord{\cdot}s^{-1}$. The experiment was repeated $50$ times, for a total of $3150$ collisions. The graphs display the speed without the random variation. The purpose of this experiment was to confirm the predicted maximum expected penetration in a centralised simulation. Fig. \ref{fig_ErrorControlDistance} shows the penetration of objects with increasing speed in a centralised simulation and demonstrates that penetration distance is never greater than the maximum expected penetration. Note that PhysX can report collisions before objects intersect, leading to the negative penetration distances shown.

As speed increases, expected penetration increases. Using penetration time gives us a uniform maximum expected value regardless of speed.
Re-arranging $s=d/t$, to $t=d/s$ and substituting the collision penetration for $d$ and speed for $s$, gives us the penetration time for a collision. It should be noted that because physics engines work in discrete time steps, this time value does not actually reflect the real time the colliding objects were penetrating each other. Correct collisions result in penetration times of up to 1 physics time step and any collision penetration times over this value are considered erroneous. Fig. \ref{fig_ErrorControlTime} shows the penetration of objects with increasing speed in a centralised simulation and demonstrates that penetration time is never greater than the time of one physics step, regardless of the relative speed of objects.

\begin{figure}[!t]
	\centering
	\includegraphics[width=\textwidth]{CentralCollisionsPenDistanceVsSpeed}
	\caption{Penetration distance of collisions with varying speed. The maximum expected penetration distance of 1 physics step is marked with a dashed blue line.}
	\label{fig_ErrorControlDistance}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{CentralCollisionsPenVsSpeed}
	\caption{Penetration time of collisions with varying speed. The maximum expected penetration time of 1 physics step is marked with a dashed blue line.}
	\label{fig_ErrorControlTime}
\end{figure}

%TODO: Outline: We've demonstrated a benchmark with which to compare distributed results with

@@

\begin{figure}
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsSpeedLow}
		\caption{$16m\mathord{\cdot}s^{-1}$}
		\label{fig_CollisionsPenVsSpeedLow}
	\end{subfigure}
	\hfill %%
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsSpeedMid}
		\caption{$32m\mathord{\cdot}s^{-1}$}
		\label{fig_CollisionsPenVsSpeedMid}
	\end{subfigure}
	\hfill %%
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsSpeedHigh}
		\caption{$48m\mathord{\cdot}s^{-1}$}
		\label{fig_CollisionsPenVsSpeedHigh}
	\end{subfigure}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeed}
\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

\begin{figure}
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsLatencyLow}
		\caption{$2ms$}
		\label{fig_CollisionsPenVsLatencyLow}
	\end{subfigure}
	\hfill %%
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsLatencyMid}
		\caption{$8ms$}
		\label{fig_CollisionsPenVsLatencyMid}
	\end{subfigure}
	\hfill %%
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsLatencyHigh}
		\caption{$16ms$}
		\label{fig_CollisionsPenVsLatencyHigh}
	\end{subfigure}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatency}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsFrameTimeLow}
		\caption{$8.33ms$}
		\label{fig_CollisionsPenVsFrameTimeLow}
	\end{subfigure}
	\hfill %%
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsFrameTimeMid}
		\caption{$15ms$}
		\label{fig_CollisionsPenVsFrameTimeMid}
	\end{subfigure}
	\hfill %%
	\begin{subfigure}[t]{0.325\columnwidth}
		\includegraphics[width=\linewidth]{MeanPenVsFrameTimeHigh}
		\caption{$33.33ms$}
		\label{fig_CollisionsPenVsFrameTimeHigh}
	\end{subfigure}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTime}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{MeanPenVsLoss}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying packet-loss. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line.}
	%\caption{Penetration time of objects with varying packet-loss. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The number and magnitude of errors increases as packet-loss increases beyond $10\%$.}
	\label{fig_CollisionsPenVsLoss}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLoss}
	\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss.} %As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
	\label{fig_RatiosVsLoss}
\end{figure}

>>>>

\subsection{Control Experiment}

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{CentralCollisionsPenDistanceVsSpeed}
	\caption{Penetration distance of collisions with varying speed. The maximum expected penetration distance of 1 physics step is marked with a dashed blue line.}
	\label{fig_ErrorControlDistance}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{CentralCollisionsPenVsSpeed}
	\caption{Penetration time of collisions with varying speed. The maximum expected penetration time of 1 physics step is marked with a dashed blue line.}
	\label{fig_ErrorControlTime}
\end{figure}

A control experiment on a centralised system (single server, single simulation) was performed, in which the scenario was repeated multiple times. The speed of each object is increased from $1$ to $64m\mathord{\cdot}s^{-1}$ in steps of $1m\mathord{\cdot}s^{-1}$. The experiment was repeated $50$ times, for a total of $3150$ collisions. The graphs display the speed without the random variation. The purpose of this experiment was to confirm the predicted maximum expected penetration in a centralised simulation. Fig. \ref{fig_ErrorControlDistance} shows the penetration of objects with increasing speed in a centralised simulation and demonstrates that penetration distance is never greater than the maximum expected penetration. Note that PhysX can report collisions before objects intersect, leading to the negative penetration distances shown.

As speed increases, expected penetration increases. Using penetration time gives us a uniform maximum expected value regardless of speed.
Re-arranging $s=d/t$, to $t=d/s$ and substituting the collision penetration for $d$ and speed for $s$, gives us the penetration time for a collision. It should be noted that because physics engines work in discrete time steps, this time value does not actually reflect the real time the colliding objects were penetrating each other. Correct collisions result in penetration times of up to 1 physics time step and any collision penetration times over this value are considered erroneous. Fig. \ref{fig_ErrorControlTime} shows the penetration of objects with increasing speed in a centralised simulation and demonstrates that penetration time is never greater than the time of one physics step, regardless of the relative speed of objects.
%TODO: Outline: We've demonstrated a benchmark with which to compare distributed results with

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. }
	\label{fig_CollisionsPenVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. $32m\mathord{\cdot}s^{-1}$}
	\label{fig_CollisionsPenVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $64m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. $48m\mathord{\cdot}s^{-1}$}
	\label{fig_CollisionsPenVsSpeedHigh}
\end{figure}
	%\label{fig_CollisionsPenVsSpeed}
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $2ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line. }
	\label{fig_CollisionsPenVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $16ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line. $48m\mathord{\cdot}s^{-1}$}
	\label{fig_CollisionsPenVsLatencyHigh}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $15ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsFrameTimeHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying frame-time using a frame-time tolerance of $32ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsFrameTimeHigh}
\end{figure}

@@

\begin{figure}[t]
	\includegraphics[width=\textwidth]{MeanPenVsLoss}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying packet-loss. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line.}
	%\caption{Penetration time of objects with varying packet-loss. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The number and magnitude of errors increases as packet-loss increases beyond $10\%$.}
	\label{fig_CollisionsPenVsLoss}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLoss}
	\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss.} %As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
	\label{fig_RatiosVsLoss}
\end{figure}
